MLH1 Results Outline

### 2020-05-01 doc/Results_v2.rmd
notes for editing results

    geom_errorbar(aes(ymin=mean_co-(se*2), ymax=mean_co+(se*2) ), width=.3, position = position_dodge(.5), size=1.001)+

@@

    theme(legend.position="none",
  panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
  panel.background = element_blank(), axis.line=element_line(colour = "black"),
  axis.title.y=element_blank(),
  axis.title.x=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank())
#remove y labfor male

   #segments
#  annotate("segment", x=.75, xend=4.5, y=19.5, yend=19.5, colour="black", size=1)+
  #Musc
#  annotate("segment", x= 5.5, xend=10.2, y=19.5, yend=19.5, colour="black", size=1)+
  #mol
#  annotate("segment", x=11, xend=12.25, y=19.5, yend=19.5, colour="black", size=1)+
  #cast
#  annotate("segment", x=13, xend=14, y=19.5, yend=19.5, colour="black", size=1)+
  #outgroups
 # annotate("segment", x=14.5, xend=16, y=19.5, yend=19.5, colour="black", size=1)+
  #label

@@

female.specific.plot <- ggplot(female_mouse.avs_for.analysis, aes(x = as.factor(strain), y = mean_co, color= strain))+ geom_boxplot()+  geom_jitter(aes( alpha=0.5), width = .2 )+ ggtitle("")+scale_color_manual(values=colors_of_strains)+ylim(c(20,34))+
  theme(legend.position="none",

        axis.title.y =element_blank(), 
      axis.text.x = element_blank(), axis.title.x = element_blank(), axis.ticks.x = element_blank(),
  panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
  panel.background = element_blank(), axis.line=element_line(colour = "black"))

@@

male.plot <- ggplot(just.male_mouse.av, aes(x = as.factor(strain), y = mean_co, color= strain))+geom_jitter( alpha=0.5, width = .2) +geom_boxplot()+ ggtitle("")+scale_color_manual(values=colors_of_strains)+ylim(c(20,34))+

   theme(legend.position="none", axis.text.x=element_blank(), axis.title.x = element_blank(), axis.ticks.x = element_blank(),  axis.title.y = element_blank(), 
  panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
  panel.background = element_blank(), axis.line=element_line(colour = "black"))

```{r Figure1.Main.plot.three.plots, echo=FALSE, warning=FALSE, fig.width=7}

@@

Figure1.main.plot + plot_annotation(
  title = '',
  subtitle = '',
  caption = 'caption'
) + plot_annotation(tag_levels = 'A')

@@

```{r Main.plot.DMC1, echo=FALSE, fig.width=6.5, fig.height=5}

@@

three.DMC1.plot + plot_annotation(
  title = '',
  subtitle = '',
  caption = 'caption'
) + plot_annotation(tag_levels = 'A')

@@

```{r Chrm.props.plot2, echo=FALSE, fig.width=8}

@@

chrm.class.barplot <- ggplot(data = chrm.class.category_MELT, aes(y = mean.percent.type, x = strain, fill=as.factor(variable)) ) + geom_col(position = "dodge")+ggtitle("")+ylim(c(0,1)) + facet_wrap(sex~subsp, scales = "free")+ theme(legend.position="none", axis.title.y = element_blank(), axis.text.x = element_text(size=9), axis.title.x = element_blank() )
#chrm.class.barplot
chrm.class.barplot

@@

Q1.SC.short.mouse_scatter_boxplot <- ggplot( Q1.real.short_mouse_table, aes(y = mean_SC, x = sex, color=strain)) + geom_jitter()+ geom_boxplot(alpha=.2) +scale_color_manual(values=colors_of_strains)+facet_wrap(~subsp, scales="free")+ylim(c(20,115) )+ggtitle("")+  theme(legend.position="none", axis.title.x = element_blank(), axis.text.x = element_text(size=9), axis.text.y = element_text(size=9))+labs(y = "Mouse Mean Short SC Length")

@@

  theme(axis.title.x=element_blank(), axis.ticks.x=element_blank(),axis.text.x = element_text(size=9), legend.position="none", axis.text.y = element_text(size=9))+  
  labs(y = "Mouse Mean Short SC Length")+
  ylim(c(1000,2600 ))+ggtitle("")

```{r Q1.Two.SC.plots, echo=FALSE, warning=FALSE, fig.width=8}

two.Q1.SC.plots <- {Q1.SC.short.mouse_scatter_boxplot + {Tot.SC_mouse.av_ALL} + plot_layout(ncol = 2, widths = c(1,1), heights = c(1.5,1.5)) }

two.Q1.SC.plots + plot_annotation(
  title = '',
  subtitle = '',
  caption = 'caption'
) + plot_annotation(tag_levels = 'A')

@@

```{r Q1.F1.pos.LONG.SHORT.BIV_scatter, echo=FALSE}

#real.long.bivData
Q1.short.biv_scatr_box   <- ggplot( (real.short.bivData %>% filter(hand.foci.count == 1) ), aes(x=sex, y=PER_Foci_1, color=strain) )+geom_jitter( )+ geom_boxplot(aes(y= PER_Foci_1 ),alpha=.3 ) + scale_color_manual(values=colors_of_strains)+facet_wrap(~subsp, scales = "free")+ylim(c(0,1.1))+ggtitle("Mouse av. \nNormalized 1CO Foci pos \nShort Biv")

@@

```{r Q1.mouse.av.F1.pos.LONG.BIV_scatter, echo=FALSE}

#REAL.short_mouse_table
#REAL.long_mouse_table
#mouse.av.long.biv.table

@@

```{r Q1.CO1_foci_pos_boxplot, echo=FALSE, eval=FALSE}

MELT_long_biv <- MELT_Curated_BivData[ MELT_Curated_BivData$Obj.ID %in% real.long.bivData$Obj.ID, ]

CO.Pos.boxplots_1CO <- ggplot(MELT_Curated_BivData.1CO, aes(x= strain, y=PER.Foci.Pos, fill=strain) ) + geom_boxplot(alpha=.2) + facet_wrap(sex~subsp, ncol=2, scales="free")+ggtitle("Percent Foci Position")+geom_jitter(alpha=.1)+scale_fill_manual(values=colors_of_strains)
CO.Pos.boxplots_1CO

```{r CO1_foci_pos_boxplot, echo=FALSE, eval=FALSE}

MELT_long_biv <- MELT_Curated_BivData[ MELT_Curated_BivData$Obj.ID %in% real.long.bivData$Obj.ID, ]

CO.Pos.boxplots_1CO <- ggplot(MELT_Curated_BivData.1CO, aes(x= strain, y=PER.Foci.Pos, fill=strain) ) + geom_boxplot(alpha=.2) + facet_wrap(sex~subsp, ncol=2, scales="free")+ggtitle("Percent Foci Position")+geom_jitter(alpha=.1)+scale_fill_manual(values=colors_of_strains)
CO.Pos.boxplots_1CO

```{r Q1.1CO.pos_Sardell.eq, echo=FALSE, eval=FALSE, include=FALSE}
#IGNORE THIS FOR KNOW, THIS

#filter all Curated biv data for 1 strain
#WSB.Bivalents.DF , use single bivalent level observations, with the strain specific DFs

# the stardell paper sums the number of COs for bins (10)

#in my data it would be like adding -- 10 more colums, and marking 1 if there is a bin within it
#but then the model would be close to logistic

#summing the number of COs per bin, losses the chrom specific data....
#!! need to use a melted Data frame to capture all nrm.foci obs
#wsb.ttest<- mouse.avs_4MM %>% filter()
#start with same chrm classes
#the telomere dist and centromere dis were celulcate for the nearest foci ... but really these shhould be calq for each foci

WSB.Biv.1CO <- WSB.Bivalents.DF %>% filter(hand.foci.count == 1)

Sardell.mo.WSB <- lmer(PER_Foci_1 ~ dis.cent + telo_dist + sex+ (1 | chromosomeLength), data = WSB.Biv.1CO)

PWD.Biv.1CO <- PWD.Bivalents.DF %>% filter(hand.foci.count == 1)

Sardell.mo.PWD <- lmer(PER_Foci_1 ~ dis.cent + telo_dist + sex + (1 | chromosomeLength), data = PWD.Biv.1CO)
Sardell.mo.PWD_R.dis.cent <- lmer(PER_Foci_1 ~  telo_dist + sex + (1 | chromosomeLength), data = PWD.Biv.1CO)
Sardell.mo.PWD_R.dis.telo <- lmer(PER_Foci_1 ~  dis.cent + sex + (1 | chromosomeLength), data = PWD.Biv.1CO)

anova(Sardell.mo.PWD,Sardell.mo.PWD_R.dis.cent) #p= highly sig

anova(Sardell.mo.PWD,Sardell.mo.PWD_R.dis.telo) #p= v low

anova(Sardell.mo.PWD_R.dis.cent, Sardell.mo.PWD_R.dis.telo) #p = 1

#or AIC(model1,model2)

@@

```{r Q1.IFD_load.triangles, echo=FALSE, message=FALSE, warning=FALSE, fig.cap = "Example of Sex differences in IFD distributions"}

@@

```{r Q2.SC_MLH1.by.totalSC, echo=FALSE, warning=FALSE, fig.height=3, fig.width=8}

@@

```{r Q2.SC.Chrm.Class, echo=FALSE, include=FALSE, eval=FALSE}
#REMOVE COMPARES ACROSS FROM FULL BIVDAAT

#1CO
log.SC_male_1CO.poly <- glm(Rec.group ~ mean.SC_1CO,
              data=Male.poly.Mouse.Table_BivData_4MM,  family=binomial(link="logit"))
#summary(log.SC_male_1CO.poly)

log.SC_male_1CO.Musc <- glm(Rec.group ~ mean.SC_1CO,
              data=Male.poly.Mouse.Table_BivData_4MM[Male.poly.Mouse.Table_BivData_4MM$subsp == "Musc",],  family=binomial(link="logit"))
#summary(log.SC_male_1CO.Musc)
#double check these directions

log.SC_male_1CO.Mol <- glm(Rec.group ~ mean.SC_1CO,
              data=Male.poly.Mouse.Table_BivData_4MM[Male.poly.Mouse.Table_BivData_4MM$subsp == "Mol",],  family=binomial(link="logit"))

#summary(log.SC_male_1CO.Mol)

#2CO
log.SC_male_2CO.poly <- glm(Rec.group ~ mean.SC_2CO,
              data=Male.poly.Mouse.Table_BivData_4MM,  family=binomial(link="logit"))
#summary(log.SC_male_2CO.poly)

log.SC_male_2CO.Musc <- glm(Rec.group ~ mean.SC_2CO,
              data=Male.poly.Mouse.Table_BivData_4MM[Male.poly.Mouse.Table_BivData_4MM$subsp == "Musc",],  family=binomial(link="logit"))
#summary(log.SC_male_2CO.Musc)

log.SC_male_2CO.Mol <- glm(Rec.group ~ mean.SC_2CO,
              data=Male.poly.Mouse.Table_BivData_4MM[Male.poly.Mouse.Table_BivData_4MM$subsp == "Mol",],  family=binomial(link="logit"))
#summary(log.SC_male_2CO.Mol)

#3CO
log.SC_male_3CO.poly <- glm(Rec.group ~ mean.SC_3CO,
              data=Male.poly.Mouse.Table_BivData_4MM,  family=binomial(link="logit"))
#summary(log.SC_male_3CO.poly)

log.SC_male_3CO.Musc <- glm(Rec.group ~ mean.SC_3CO,
              data=Male.poly.Mouse.Table_BivData_4MM[Male.poly.Mouse.Table_BivData_4MM$subsp == "Musc",],  family=binomial(link="logit"))
#summary(log.SC_male_3CO.Musc)

#there's no rec group for this table
log.SC_male_3CO.Mol <- glm(Rec.group ~ mean.SC_3CO,
              data=Male.poly.Mouse.Table_BivData_4MM[Male.poly.Mouse.Table_BivData_4MM$subsp == "Mol",],  family=binomial(link="logit"))
#summary(log.SC_male_3CO.Mol)

#reverse logistic regression (single bivalent level)
#how well does SC length predict 1 or 2 COs?

Bivalent_1o2 <-  Curated_BivData_male %>% filter(species== "M.musculus") %>% filter(hand.foci.count > 0) %>% filter(hand.foci.count < 3)

#need to switch the co counts to 1 - 0
Bivalent_1o2$chrm.class <- ifelse(grepl(1, Bivalent_1o2$hand.foci.count), 0, 
                                    ifelse(grepl(2, Bivalent_1o2$hand.foci.count), 1, ""))

Bivalent_1o2$chrm.class <- as.numeric(Bivalent_1o2$chrm.class)
Bivalent_1o2$strain <- factor(Bivalent_1o2$strain, ordered = FALSE)

log.SC_male_chrm.class <- glm(chrm.class ~ chromosomeLength*strain,
              data=Bivalent_1o2,  family=binomial(link="logit"))

summary(log.SC_male_chrm.class)
#not sure if this is the equivilent of running each strain seperatly
#the strain effect is probably also pulling in the different proportion of chrm class
#useing the chrm.length*strain gives fewer significant factors.

#i'd be more convinced by running all those log regression plots for each strain
#come back later
```

@@

```{r Q2.SClength.ttest, echo=FALSE, include=FALSE, eval=FALSE}
#COMPARISONS ACROSS ALL CLASSES

#MOUSE AVE, all
Rec.group.mouse.SC_Ttest <- t.test(Male.poly.Mouse.Table_BivData_4MM$mean_SC[Male.poly.Mouse.Table_BivData_4MM$Rec.group == 1], 
                                 Male.poly.Mouse.Table_BivData_4MM$mean_SC[Male.poly.Mouse.Table_BivData_4MM$Rec.group == 0])

Rec.group.mouse.SC_Ttest$p.value  #p-value = 0.00238

#mouse.av 1CO
Rec.group.mouse.SC.1CO_Ttest <- t.test(Male.poly.Mouse.Table_BivData_4MM$mean.SC_1CO[Male.poly.Mouse.Table_BivData_4MM$Rec.group == 1], 
                                 Male.poly.Mouse.Table_BivData_4MM$mean.SC_1CO[Male.poly.Mouse.Table_BivData_4MM$Rec.group == 0])

Rec.group.mouse.SC.1CO_Ttest$p.value  #p-value = 0.9993

#MOUSE.av 2CO
Rec.group.mouse.SC.2CO_Ttest <- t.test(Male.poly.Mouse.Table_BivData_4MM$mean.SC_2CO[Male.poly.Mouse.Table_BivData_4MM$Rec.group == 1], 
                                 Male.poly.Mouse.Table_BivData_4MM$mean.SC_2CO[Male.poly.Mouse.Table_BivData_4MM$Rec.group == 0])

Rec.group.mouse.SC.2CO_Ttest$p.value  #p-value = 0.03428

#single biv level
#male.biv?

#Rec.group_BivData_F1post_Ttest <- t.test(male.bivdata.1CO$PER_Foci_1[male.bivdata.1CO$Rec.group == 1], 
#                                 male.bivdata.1CO$PER_Foci_1[male.bivdata.1CO$Rec.group == 0])

#Rec.group_BivData_F1post_Ttest$p.value

@@

```{r male.show.plotsEXample, echo=FALSE, eval=FALSE}
male_mouse.av <- subset(AP_mouse_table_w.Ages, select= -c(sex.y,sex.x,
                            subsp.y,subsp.x,
                    category.y,category.x, strain.x,
                    strain.y, mouse.1  )  )

male_mouse.av <- add_sex(male_mouse.av)
male_mouse.av <- add_strain(male_mouse.av)
male_mouse.av <- add_subsp(male_mouse.av)
male_mouse.av <- add_species(male_mouse.av)

fomo.male_mouse.av <-  male_mouse.av %>% filter(sex== "male") %>% filter(species == "M.musculus")

fomo.male_mouse.av$subsp <- factor(fomo.male_mouse.av$subsp, ordered = FALSE)
fomo.male_mouse.av$sex <- factor(fomo.male_mouse.av$sex, ordered = FALSE)
fomo.male_mouse.av$strain <- factor(fomo.male_mouse.av$strain, ordered = FALSE)
fomo.male_mouse.av$species <- factor(fomo.male_mouse.av$species, ordered = FALSE)

#make the Mol and
Mol.male_mouse.av <-  fomo.male_mouse.av %>% filter(sex== "male") %>% filter(subsp == "Mol")

Mol.male.plot <- ggplot(Mol.male_mouse.av, aes(color= strain))+geom_jitter(aes(x = as.factor(strain), y = mean_co, color= strain, alpha=0.5), width = .2 )+ ggtitle("Mol male of MLH1 distributions")+scale_color_manual(values=colors_of_strains)+ylim(c(20,33))

#Dom version 
Dom.male_mouse.av <-  fomo.male_mouse.av %>% filter(sex== "male") %>% filter(subsp == "Dom")

Dom.male.plot <- ggplot(Dom.male_mouse.av, aes(color= strain))+geom_jitter(aes(x = as.factor(strain), y = mean_co, color= strain, alpha=0.5), width = .2 )+ ggtitle("Dom male of MLH1 distributions")+scale_color_manual(values=colors_of_strains)+ylim(c(20,33))

@@

```{r Q2.1CO.show_plots, echo=FALSE,  warning=FALSE}
#Curated_BivData_male

@@

Q2.show.nrmF1 <- ggplot(male.bivdata.1CO, aes(x=strain, y=PER_Foci_1, color=strain) )+geom_jitter(alpha=.5 )+ geom_boxplot(aes(y= PER_Foci_1), alpha=.3 ) + scale_color_manual(values=colors_of_strains)+facet_wrap(~subsp, scales = "free")+ylim(c(0,1.1))+theme(legend.position="none", axis.text.x = element_text(size=9), axis.title.x = element_blank())+labs(y="Foci 1 Relative Position")

@@

```{r Q2.IFD_load.triangles, echo=FALSE, message=FALSE, warning=FALSE, fig.width=6}

@@

```{r double.IFD.triangle_copy, echo=FALSE, eval=FALSE}

```{r Q1.IFD_load.triangles.copy, echo=FALSE, message=FALSE, warning=FALSE, fig.cap = "Example of Sex differences in IFD distributions", eval=FALSE}

>>>>

    geom_errorbar(aes(ymin=mean_co-(se*2), ymax=mean_co+(se*2) ), width=.3, position = position_dodge(.5), size=1)+

@@

    theme(legend.position="none",
  panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
  panel.background = element_blank(), axis.line=element_line(colour = "black"),
  axis.title.y=element_blank(),
  axis.title.x=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank())+
#remove y labfor male

   #segments
  annotate("segment", x=.75, xend=4.5, y=19.5, yend=19.5, colour="black", size=1)+
  #Musc
  annotate("segment", x= 5.5, xend=10.2, y=19.5, yend=19.5, colour="black", size=1)
  #mol
#  annotate("segment", x=11, xend=12.25, y=19.5, yend=19.5, colour="black", size=1)+
  #cast
#  annotate("segment", x=13, xend=14, y=19.5, yend=19.5, colour="black", size=1)+
  #outgroups
 # annotate("segment", x=14.5, xend=16, y=19.5, yend=19.5, colour="black", size=1)+
  #label

@@

female.specific.plot <- ggplot(female_mouse.avs_for.analysis, aes(x = as.factor(strain), y = mean_co, color= strain))+ geom_boxplot()+  geom_jitter(aes( alpha=0.5), width = .2 )+ ggtitle("")+scale_color_manual(values=colors_of_strains)+ylim(c(17,34))+
  theme(legend.position="none",

        axis.title.y =element_blank(), 
      axis.text.x = element_blank(), axis.title.x = element_blank(), axis.ticks.x = element_blank(),
  panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
  panel.background = element_blank(), axis.line=element_line(colour = "black"))+geom_hline(yintercept = 20)

@@

male.plot <- ggplot(just.male_mouse.av, aes(x = as.factor(strain), y = mean_co, color= strain))+geom_jitter( alpha=0.5, width = .2) +geom_boxplot()+ ggtitle("")+scale_color_manual(values=colors_of_strains)+ylim(c(17,34))+

   theme(legend.position="none", axis.text.x=element_blank(), axis.title.x = element_blank(), axis.ticks.x = element_blank(),  axis.title.y = element_blank(), 
  panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
  panel.background = element_blank(), axis.line=element_line(colour = "black"))+geom_hline(yintercept = 19)

#horizontal line = 20

```{r Figure1.Main.plot.three.plots, echo=FALSE, warning=FALSE, fig.width=7, fig.cap='*Figure 1 Mean MLH1 count distributions by strain.* A) Strain averages of MLH1 counts per cell. B) Female specific MLH1 count distributions. C)	Male specific MLH1 counts per cell.'}

@@

Figure1.main.plot + plot_annotation(
  title = '',
  subtitle = '',
  caption = ''
) + plot_annotation(tag_levels = 'A')

@@

```{r Main.plot.DMC1, echo=FALSE, fig.width=6.5, fig.height=5, fig.cap="*Figure 2 male DSB estimates* A) Example early zygotene spermatocyte spread, B) Example late zygotene spermatocyte spread. Green foci show DMC1. B)	Distribution of DMC1 counts per cell  by strains. (1 mouse was used for each strain)"}

@@

three.DMC1.plot + plot_annotation(
  title = '',
  subtitle = '') + plot_annotation(tag_levels = 'A')

@@

```{r Chrm.props.plot2, echo=FALSE, fig.width=8, fig.cap="*Figure 3* Chromosome Class Proportions. proportions calculated from pooled single bivalent data by strain."}

@@

chrm.class.barplot <- ggplot( data = (chrm.class.category_MELT %>% filter(strain != "CZECH")),
                             aes(y = mean.percent.type, x = strain, fill=as.factor(variable)) ) + geom_col(position = "dodge")+ggtitle("")+ylim(c(0,1)) + facet_wrap(sex~subsp, scales = "free")+ theme(legend.position="top", legend.title = element_blank(), 
                                                                                                           axis.title.y = element_blank(), axis.text.x = element_text(size=9), axis.title.x = element_blank() )+scale_fill_discrete(name = "Chromosome Class", labels =c('0CO','1CO','2CO','3CO','4CO') )

chrm.class.barplot
kk <- addSmallLegend(chrm.class.barplot)

@@

Q1.SC.short.mouse_scatter_boxplot <- ggplot( Q1.real.short_mouse_table, aes(y = mean_SC, x = sex, color=strain)) + geom_jitter()+ geom_boxplot(alpha=.2) +scale_color_manual(values=colors_of_strains)+facet_wrap(~subsp, scales="free")+ylim(c(20,115) )+ggtitle("")+  theme(legend.position="none", axis.title.x = element_blank(), axis.text.x = element_text(size=9), axis.title.y = element_text(size = 10), axis.text.y = element_text(size=9))+labs(y = "Mouse Mean Short SC Length")

@@

  theme(axis.title.x=element_blank(), axis.ticks.x=element_blank(),axis.text.x = element_text(size=9), legend.position="none", axis.text.y = element_text(size=9), axis.title.y = element_text(size = 10)  )+  
  labs(y = "Mouse Mean Total SC Length")+
  ylim(c(1000,2600 ))+ggtitle("")

```{r Q1.Two.SC.plots, echo=FALSE, warning=FALSE, fig.width=8, fig.cap= 'caption'}

two.Q1.SC.plots <- {Q1.SC.short.mouse_scatter_boxplot + {Tot.SC_mouse.av_ALL} + plot_layout(ncol = 2, widths = c(1,1), heights = c(2,2)) }

two.Q1.SC.plots + plot_annotation(
  title = '',
  subtitle = '') + plot_annotation(tag_levels = 'A')

@@

```{r Q1.F1.pos.LONG.SHORT.BIV_scatter, echo=FALSE}
#real.long.bivData
Q1.short.biv_scatr_box   <- ggplot( (real.short.bivData %>% filter(hand.foci.count == 1) ), aes(x=sex, y=PER_Foci_1, color=strain) )+geom_jitter( )+ geom_boxplot(aes(y= PER_Foci_1 ),alpha=.3 ) + scale_color_manual(values=colors_of_strains)+facet_wrap(~subsp, scales = "free")+ylim(c(0,1.1))+ggtitle("Mouse av. \nNormalized 1CO Foci pos \nShort Biv")

@@

```{r Q1.mouse.av.F1.pos.LONG.BIV_scatter, echo=FALSE}
#REAL.short_mouse_table
#REAL.long_mouse_table
#mouse.av.long.biv.table

@@

@@

```{r Q1.IFD_load.triangles, echo=FALSE, message=FALSE, warning=FALSE, fig.cap = "Distribution of normalized foci positions (IFDs) for double crossover bivalents across sexes. Female and male patterns are displayed in the top and bottom triangle respectively. Each point reflects a single double crossover bivalent, with the normalized positions of foci reflected on each axis."}

@@

mouse.av_totsc_male <- addSmallLegend(mouse.av_totsc_male)

```{r Q2.SC_MLH1.by.totalSC, echo=FALSE, warning=FALSE, fig.height=3, fig.width=8, fig.cap="Variation in total SC area per cell across strains and Relationship between total sc and mean MLH1 count per cell across male mice. A)	 Mean total SC area per mouse across subspecies and recombination groups. High- and low-recombining groups are indicated by 1 and 0 respectively. (Horizontal lines indicate strain averages for total SC area.)B) Mouse averaged rates of MLH1 and total SC per cell"}

@@

@@

@@

@@

```{r Q2.1CO.show_plots, echo=FALSE,  warning=FALSE, fig.cap="Male distributions of single crossover normalized positions.", fig.width=4}
#Curated_BivData_male

@@

Q2.show.nrmF1 <- ggplot(male.bivdata.1CO, aes(x=strain, y=PER_Foci_1, color=strain) )+geom_jitter(alpha=.23 )+ geom_boxplot(aes(y= PER_Foci_1), alpha=.5 ) + scale_color_manual(values=colors_of_strains)+facet_wrap(~subsp, scales = "free")+ylim(c(0,1.1))+theme(legend.position="none", axis.text.x = element_text(size=9), axis.title.x = element_blank())+labs(y="Foci 1 Relative Position")

@@

```{r Q2.IFD_load.triangles, echo=FALSE, message=FALSE, warning=FALSE, fig.width=6, fig.cap="male IFD distributions highlighting differences across recombining groups"}

@@
